A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-05 Paper.tex
Latest

\section{Beacon Initialization}
Beacons initialization refers to the precursor process to the EKF where beacons (or landmarks) whose initial positions are not known are estimated. One of the complications with RO-SLAM involves the issue of the EKF, which is used by many implementations, being  sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These methods are further  divided into delayed and undelayed initializations.
\subsection{Delayed/Offline initializations}
These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks. This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles. Localization can be performed only once a accurate estimations of the beacons are made. There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{} , a moving horizon estimation as mentioned in [9] etc. The most popular ones are mentioned below.

@@

Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented. An IF algorithm is mentioned in\cite{Torres-Gonzalez2014}. In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa. Hence they are dual to each other.
Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix. This makes the SEIF more scalable and effiecient as show in\cite{Torres-Gonzalez2014}

@@

In \cite{Torres-Gonzalez2014} they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process. Hence the computer burden on the robot is reduced. In addition they factored in inter beacon measurements to reduce uncertainity even furthur. In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.

@@

It represents the information in the form of a graph as show in figure. The nodes in the graph represent the robots path and the landmarks. The edges between them represents the spatial  constraints between them also known as information constraints. These constraints ae then linearised and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in [ turorial in graph slam].

@@

As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment. 
EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}
As the number of particles increases the computational complexity of the filter too increases. In order to address this there were several new methods introduced that  exploit the independence among state variables. For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from [Fast slam paper]. It also solves the data association problem previously unsolved by EKF[need to add paper].

@@

	FastSLAM utilizes the conditional Independence property of SLAM applications. If the path of the robot is known the correlation between the landmarks becomes zero. Hence in FastSLAM the robot path is initialised by using a particle fitler. Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{}. Thus it maintains mutliple data hypothesis overcoming the EKF problem.

>>>>

\section{Beacon Initialization}
Beacons initialization refers to the precursor process to the EKF where beacons (or landmarks) whose initial positions are not known are estimated. One of the complications with RO-SLAM involves the issue of the EKF, which is used by many implementations, being  sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These methods are further  divided into delayed and undelayed initializations.
\subsection{Delayed/Offline initializations}
These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks. This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles. Localization can be performed only once a accurate estimations of the beacons are made. There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{Webster} , a moving horizon estimation as mentioned in \cite{SenWang2013} etc. The most popular ones are mentioned below.

@@

Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented. An IF algorithm is mentioned in\cite{Torres-Gonzalez2014}. In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa. Hence they are dual to each other.
Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix. This makes the SEIF more scalable and efficient as show in\cite{Torres-Gonzalez2014}

@@

In \cite{Torres-Gonzalez2014} they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process. Hence the computer burden on the robot is reduced. In addition they factored in inter beacon measurements to reduce uncertainity even furthur. In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM mehtod using EKF.

@@

It represents the information in the form of a graph as show in figure. The nodes in the graph represent the robots path and the landmarks. The edges between them represents the spatial  constraints between them also known as information constraints. These constraints ae then linearised and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in \cite{Grisetti}.

@@

As mentioned in \cite{Thrun2002a} particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment. 
EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}
As the number of particles increases the computational complexity of the filter too increases. In order to address this there were several new methods introduced that  exploit the independence among state variables. For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from \cite{Yuan2012}. It also solves the data association problem previously unsolved by EKF.

@@

	FastSLAM utilizes the conditional Independence property of SLAM applications. If the path of the robot is known the correlation between the landmarks becomes zero. Hence in FastSLAM the robot path is initialised by using a particle fitler. Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{Yuan2012}. Thus it maintains mutliple data hypothesis overcoming the EKF problem.
